Hybrid platforms and bargaining power

### 2022-12-15 src/paper/application.tex
Fix equation for equilibrium entry
Flesh out the benchmark case a bit more

For ease of notation, let us define the following:
\begin{align*}
    V_T = \exp \left( \frac{v_T - c_T - \mu}{\mu} \right).
\end{align*}
Then, equilibrium per-product demand and variable profit can be expressed as $V_T/ A$ and $\mu V_T/ A$, respectively.

@@

Recall that there is an infinity of potential fringe entrants looking to enter the market.
Therefore, total profits in equilibrium must be zero.
Let us for the moment assume that fixed fees are low enough for some fringe firms to enter the market.
In this case, setting $\pi^{t*}_F$, equation \eqref{eq:fringe_profit} implies that the size of the aggregate is
\begin{align}
    A = \mu \frac{V_F}{F_F + I_F}.
    \label{eq:aggregate_eq}
\end{align}
Substituting this into equation \eqref{eq:aggregate} and rearranging gives the number of fringe firms that enter the market:
\begin{align*}
    N_F = \frac{\mu}{F_F + I_F} - I_F N_P \frac{V_P}{V_F} - \frac{1}{V_F}.
\end{align*}

@@

Combining these two, the platform's total profit as a function of the entry fee can be expressed as
\begin{align*}
    \pi_P^{t} = \mu\frac{F_F}{F_F + I_F} + N_P I_F \frac{V_P}{V_F} - \frac{F_F}{V_F}
\end{align*}

Now let us consider the case when the fringe is not present in the market.
In this case, the collected entry fees are obviously zero, and the platform's profit is simply given by
\begin{align*}
    \pi_P^{t} = \pi_P^{v} = \mu \frac{ N_P V_P}{N_P V_P + 1}.
\end{align*}

Note, that even though the platform's profit is increasing in the number of its products, the optimal entry fee does not depend on it.
As a consequence, the size of the aggregate, and hence consumer welfare is also unaffected by the platform operating in hybrid mode.
% TODO: intuition
% TODO: when does switching to retail mode occur?

>>>>

For ease of notation, let us define the following:
\begin{align*}
    V_T = \exp \left( \frac{v_T - c_T - \mu}{\mu} \right).
\end{align*}
Then, equilibrium per-product demand and variable profit can be expressed as $V_T/ A$ and $\mu V_T/ A$, respectively, and the total aggregate is simply
\begin{align*}
    A = N_P V_P + N_F V_F + 1.
\end{align*}

@@

Recall that there is an infinity of potential fringe entrants looking to enter the market.
Therefore, total profits in equilibrium must be zero.
Let us for the moment assume that fixed fees are low enough for some fringe firms to enter the market.
In this case, setting $\pi^{t*}_F$, equation \eqref{eq:fringe_profit} implies that the size of the aggregate is
\begin{align}
    A = \mu \frac{V_F}{F_F + I_F}.
    \label{eq:aggregate_eq}
\end{align}
Substituting this into equation \eqref{eq:aggregate} and rearranging gives the number of fringe firms that enter the market:
\begin{align*}
    N_F = \frac{\mu}{F_F + I_F} - N_P \frac{V_P}{V_F} - \frac{1}{V_F}.
\end{align*}

@@

Combining these two, the platform's total profit as a function of the entry fee can be expressed as
\begin{align}
    \pi_P^{t} = \mu\frac{F_F}{F_F + I_F} + N_P I_F \frac{V_P}{V_F} - \frac{F_F}{V_F}
    \label{eq:hybrid_profit}
\end{align}
Note, that even though the platform's profit is increasing in the number of its products, the optimal entry fee does not depend on it.
In particular, the optimal entry fee is given by
\begin{align*}
    F_F^* = \sqrt{\mu I_F V_F} - I_F.
\end{align*}
As a consequence, as long as the fringe is feasible at the optimal entry fee, the size of the aggregate, and hence consumer welfare is also unaffected by the platform operating in hybrid mode.
Substituting it into the profit function, the maximized profit is
\begin{align*}
    \pi_P^{t} = \mu - 2\sqrt{\frac{I_F \mu}{V_F}} + \frac{I_F}{V_F} (N_P V_P + 1).
\end{align*}

Now let us consider the case when the fringe is not present in the market.
In this case, the collected entry fees are obviously zero, and the platform's profit is simply given by
\begin{align*}
    \pi_P^{t} = \pi_P^{v} = \mu \frac{ N_P V_P}{N_P V_P + 1}.
\end{align*}
In this regime, total aggregate, and hence consumer welfare are increasing in the number of the platform's products.
This is mechanical: more variety leads to higher welfare.

Finally, note that the profit of the platform in the hybrid regime is higher than in the retail regime, when the former is feasible.
This is a consequence of the fact that equation \eqref{eq:hybrid_profit} is strictly concave in $F_F$, therefore $F_F^*$ is a global maximum.
It implies that there is no jump in no point where the fringe would be feasible under optimal entry fees, but the platform would prefer to operate in retail mode.
Therefore, in the benchmark model, a platform becomes a hybrid platform, or increasing the number of its own products, always has a weakly positive effect on the aggregate, and thus consumer welfare.
This is in contrast to \textcite{anderson2021hybrid}, where a platform operating in hybrid mode sets a higher entry fee to advantage its own products, which in turn leads to a smaller aggregate.

% TODO: intuition
